---
title: "DS202 Homework 5"
author: "Scott Madland, Wave"
date: "2023-03-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```


## Question Set 1 

1. What is the overall number of chocolate bars rated? 
```{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
summary(choco)

# 1852 total chocolate bars rated in the data set 

```

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports. 
```{r}

ggplot(data = choco, aes(x=Review.Date , y=Rating)) + 
  geom_bar(stat = 'identity')


```


## Question Set 2

For each of the questions below provide at least one graphic as a basis for your answer.

1. How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.
```{r}
ggplot(choco , aes(x = Rating)) + geom_histogram(bins = 12)

```


The ratings are the highest at around 2.75 and 3.75. The outlier seems to be the rating 5.

2. Do ratings depend on the cocoa percentage of a chocolate bar?
```{r}
ggplot(data =choco ,aes(x = Cocoa.Pct , y= Rating)) + geom_point() + geom_smooth(method=lm, se=FALSE)

```


It does not seems like the rating depends on the cocoa percentage of the chocolate bar.

3. How do ratings compare across different company locations? Focus on the three locations with the most ratings:
```{r}
fChoco<-dplyr :: filter (choco, Company.Location %in% c("U.S.A.", "France","Canada"))
ggplot(data =fChoco ,aes(x=Rating,fill= Company.Location)) +geom_bar(position = "dodge")

```


It seems that the highest rating in USA is about 3.75, the highest in France is about 3.75 as well, and in Canada is also 3.25.

## Your Own Question

Scott's Question: Which cocoa percentage results in the highest ratings? Use a bar chart to display the comparison.  


```{r}
ggplot(data = choco, aes(x=Cocoa.Pct , y=Rating)) + 
  geom_bar(stat = 'identity')

# Clearly somewhere close to 70% is the ideal cocoa percentage for achieving the highest rating on average 

```


Wave's Question: How high the cocoa percentage in the chocolate bar is the most commonly used in the USA
```{r}
UChoco<-dplyr :: filter (choco, Company.Location %in% c("U.S.A."))
ggplot(data =UChoco ,aes(x=Cocoa.Pct,fill= Company.Location)) +geom_bar()
```


It seems that 70% cocoa percentage is most commonly used by the USA to make chocolate bars


## Submission 


Link to github repo: https://github.com/ScottMadland/DS202-Homework

https://github.com/Towave28/DS202-Homework



Paragraph commenting on workflow: 

Github and Rstudio allow us to seamlessly work with many different kinds of files at the exact same time 
other people are as well. It makes it very easy for group work on any of the homework assignments for this 
course. A couple emails and github messages and before you know it a beautiful Rmarkdown and HTML document 
are created. Both of the interfaces work very well together and allow for easy collaboration. Pushing and pulling allows us to make changes quickly and often. My partner and I are both looking forward to continuing to use both of these platforms to complete assignments for the rest of this course and throughout our careers. 


