---
title: "DS202 Homework 5"
author: "Scott Madland, Wave"
date: "2023-03-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```


## Question Set 1 

1. What is the overall number of chocolate bars rated? 
```{r}


```

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports. 
```{r}


```


## Question Set 2

For each of the questions below provide at least one graphic as a basis for your answer.

1. How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.
```{r}


```

2. Do ratings depend on the cocoa percentage of a chocolate bar?
```{r}


```

3. How do ratings compare across different company locations? Focus on the three locations with the most ratings:
```{r}


```


## Your Own Question

Scott's Question: 
```{r}


```


Wave's Question: 
```{r}


```



## Submission 


Link to github repo: 



Paragraph commenting on workflow: 




